Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-06-14 hpmoon-hpca.tex
Changed bibliography style to Vancouver

\documentclass[Afour,sageh,times]{sagej}

\usepackage{moreverb,url,color}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

@@

Multi-objective optimization problems (MOP) are those where several objectives have to be simultaneously optimized \cite{Mora13paretobased}. Solving a MOP implies maximize or minimize a function composed of several cost functions (one per objective). In these problems the aim is to obtain a set of solutions that are better than the rest, considering all the objectives; this set is known as the Pareto Front. The solutions in this set are {\em non-dominated}, that is, none is better than the others for all the objectives. MOEAs are sub-set of EAs used to solve MOPs. One of the most well-known and referenced MOEAs \cite{Dorronsoro13superlinear} is the {\em Non-dominated Sorting Genetic Algorithm} (NSGA-II) \cite{Deb00NSGAII}. Classical genetic operators are applied to all the individuals, and divided into different ranks (based on the dominance) to be selected for the next generations.

@@

To solve this issue, some authors have proposed the usage of Master-Slave approaches. For example,  \cite{Durillo08masterslave} compared different master-slave approaches {\color{red} TODO DESCRIBIR MEJOR ESTE TRABAJO}. The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power {\color{red} TODO Y ESTE}.

The work by \cite{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs). In that work, the dominance of solutions was divided into the islands using a transformation of coordinates. Their authors concluded that dividing the search space is a good idea, but achieve this is not trivial. Other approaches for dividing the search space include objective separation in different processors \citep{Xiao03specialized}, or divide in two populations: one for elite and other search \citep{Wang09parallel}. Martens, in \citep{Martens13asynchronous} generated a Barabasi-Albert network as the island topology, and selection based on migrating individuals from a not-crowded area and acceptance based on diversity.

More similar approaches to the one presented here were studied in the
next two works, also using cooperative coevolution for high-dimensional problems. 
\cite{Dorronsoro13superlinear} obtained super-linear performance
in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version 
improved the sequential version.  \cite{Kimovski15Parallel} proposed a
master-slave method that splits the population into several processors,
each one running in parallel a MOEA that only affects some portion of
the individuals. After a certain number of generations, the master
process receives all the sub-populations to be combined. Different
combination alternatives in this step are compared. Up to 8 processors
were used in the experimental setup. Our approach in this paper does not
broadcast all solutions to all islands for recombination, as previous
works, but only one solution to a random island, needing less
communication time. Besides, the maximum number of islands of
Dorronsoro or Kimovsky approaches was 8, while in this paper we have
used up to 128 islands.

@@

As in the baseline, every certain number of generations, an individual is migrated to another random island.  In the new island, this individual will be considered as one of the others in the island, crossed and mutated in the same way, depending of the island identifier. Note that, on the contrary of other works such as the ones described by \cite{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.

@@

Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller. This is consistent with the claim by \cite{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).

@@

\bibliographystyle{SageH}

>>>>

\documentclass[Afour,sagev,times]{sagej}

\usepackage{moreverb,url,color}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

@@

Multi-objective optimization problems (MOP) are those where several objectives have to be simultaneously optimized \citep{Mora13paretobased}. Solving a MOP implies maximize or minimize a function composed of several cost functions (one per objective). In these problems the aim is to obtain a set of solutions that are better than the rest, considering all the objectives; this set is known as the Pareto Front. The solutions in this set are {\em non-dominated}, that is, none is better than the others for all the objectives. MOEAs are sub-set of EAs used to solve MOPs. One of the most well-known and referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em Non-dominated Sorting Genetic Algorithm} (NSGA-II) \citep{Deb00NSGAII}. Classical genetic operators are applied to all the individuals, and divided into different ranks (based on the dominance) to be selected for the next generations.

@@

To solve this issue, some authors have proposed the usage of Master-Slave approaches. For example,  \citep{Durillo08masterslave} compared different master-slave approaches {\color{red} TODO DESCRIBIR MEJOR ESTE TRABAJO}. The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power {\color{red} TODO Y ESTE}.

The work by Deb et al. \citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs). In that work, the dominance of solutions was divided into the islands using a transformation of coordinates. Their authors concluded that dividing the search space is a good idea, but achieve this is not trivial. Other approaches for dividing the search space include objective separation in different processors \citep{Xiao03specialized}, or divide in two populations: one for elite and other search \citep{Wang09parallel}. Martens, in \citep{Martens13asynchronous} generated a Barabasi-Albert network as the island topology, and selection based on migrating individuals from a not-crowded area and acceptance based on diversity.

More similar approaches to the one presented here were studied in the
next two works, also using cooperative coevolution for high-dimensional problems. 
Dorronsoro et al. \citep{Dorronsoro13superlinear} obtained super-linear performance
in several instances using cooperative coevolution, focusing each island on a portion of the chromosome. However, in some instances the parallel version 
improved the sequential version. Kimovski et al. \citep{Kimovski15Parallel} proposed a
master-slave method that splits the population into several processors,
each one running in parallel a MOEA that only affects some portion of
the individuals. After a certain number of generations, the master
process receives all the sub-populations to be combined. Different
combination alternatives in this step are compared. Up to 8 processors
were used in the experimental setup. Our approach in this paper does not
broadcast all solutions to all islands for recombination, as previous
works, but only one solution to a random island, needing less
communication time. Besides, the maximum number of islands of
Dorronsoro or Kimovsky approaches was 8, while in this paper we have
used up to 128 islands.

@@

As in the baseline, every certain number of generations, an individual is migrated to another random island.  In the new island, this individual will be considered as one of the others in the island, crossed and mutated in the same way, depending of the island identifier. Note that, on the contrary of other works such as the ones described by Talbi et al. \citep{Talbi08Parallel} all the islands deal with complete chromosomes for fitness calculation, so our approach can deal with no decomposable problems.

@@

Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller. This is consistent with the claim by Dorronsoro et al. \citep{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).

@@

\bibliographystyle{SageV}
